---
title: "Fun Application for Course Project: Shiny Application and Reproducible Pitch"
author: "Gongyao Wang"
date: "February 25, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```


## Introduction
- This Fun Application was built for the course project: Shiny Application and Reproducible Pitch. This Application is providing you some ways to predict the Horsepower based on MPG. It includes two parts: (1) Shiny Application and (2) Reproducible Pitch Presentation.

- My developed Shiny Application is avalilable at: https://gwangshare.shinyapps.io/funapp/

- My Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/gongyaowang/course9assignment3


## Fun Application Functions {.smaller}
The main functions include:

1. you can choose options to customize the figure.
    + Show/Hide X Axis Label
    + Show/Hide Y Axis Label
    + Show/Hide Title
2. you have options to adjust models.
    + Show/Hide Model 1 line
    + Show/Hide Model 2 line
    + MPG number for Model 2 (Ranging from 17 to 25), which you can use to find the best model.
3. You can get the predicted Horsepower for your models based on the MPG that you sleceted.


## Dataset for the Current Application {.smaller}

The mtcars dataset used in the application comes from the Motor Trend Car Road Tests data. Here is the data summary:
```{r}
summary(mtcars)
```

## Data Plot
Here is the data plot for the models (1. polynomial, 2. two linear).
```{r}
plot(mtcars$mpg, mtcars$hp, xlab = "Miles Per Gallon",
    ylab = "Horsepower", main = "Car MPG vs. Horsepower Models", 
    bty = "n", pch = 16, xlim = c(10, 35), ylim = c(50, 350))

```






